%-------------------------
% Resume in Latex
% Author : Gabriel Sison
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Random Stuff %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Commands  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{-3pt}
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{0pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Heading  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
    \begin{center}
        % NAME
        {\Huge\scshape Kent K.C. Ho} 
        % % SUBHEADING
        
        % \small
        % EMAIL
        \href{mailto:ho.kimcang@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ho.kimcang@gmail.com}} ~
        % LINKEDIN
        \href{https://www.linkedin.com/in/kentkcho/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/kentkcho}}  ~
        
        % GITHUB
        \href{https://github.com/kimcangho}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/kimcangho}}
        % Portfolio
        \href{https://kent-kc-ho-portfolio.webflow.io/}{\raisebox{-0.2\height}\faGlobe\ \underline{kent-kc-ho-portfolio.webflow.io}}

        \vspace*{0.2cm} {Toronto, ON, Canada }
    \end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Technical Skills  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}

    \vspace{-7pt}
    \begin{itemize}
    [leftmargin=0.15in, label={}]\small{\item{
        % Core Skills
        \textbf{Core Skills}{: JavaScript, TypeScript, React, TailwindCSS, SASS, CSS3, HTML5, Node.js, Express.js, Prisma, MySQL, JWT, Socket.io, Vite, Git, Github} \\
        % Exposed to
        \textbf{Exposed to}{: Next.js, Vercel, Bootstrap, MongoDB, Python, Figma} \\
    \end{itemize}
 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Experience  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
    \resumeSubHeadingListStart
    
        % Position 1
        \resumeSubheading
        {Software Engineering Teaching Assistant (Full-time Contract)}{Toronto, ON}
            % COMPANY 1
            {BrainStation - HTML, CSS, SASS, JavaScript, React, Node.js, Express.js, MySQL, JWT, JIRA}{01/2023 - 04/2023}
            \resumeItemListStart
                \resumeItem{Directed a cohort of 38 software engineering boot camp students by kicking off projects and clarifying scope requirements. Supported cross-collaborative teams (UX designers, data scientists and software engineers) for hackathons and managed project sprints using scrum and agile methodology.}
                \resumeItem{Debugged student projects and lab assignments. Reviewed project code and for student weekly deliverables and provided actionable feedback to bolster technical understanding and code readability. Empowered students to refine capstone project development by providing insights to relevant technologies and libraries.}
                \resumeItem{Conducted review sessions to reinforce web development concepts through interactive quizzes, live code-alongs and technical interview practice.}
            \resumeItemListEnd

        % POSITION 2
        \resumeSubheading
        {Water Operator (Operator-In-Training / I / II)}{Vaughan, ON}
            % COMPANY 2
            {City of Vaughan - Python}{10/2019 - 07/2022}
            \resumeItemListStart
                \resumeItem{Refined operator time card spreadsheet with quality of life features (autofilling, mass cell deletions, save and quit buttons) using VBA macros. Automated  workflow using Python batch file to fetch local time cards, convert file format and submit through email using Gmail SMTP. Reduced water operations paperwork overhead time by 15 hours per week and entrusted to optimize team lead internal tracking tools.}
                \resumeItem{Investigated water sampling stations due to non-compliant water contaminant levels. Devised and executed quality assurance procedure to extract, rebuild and test appurtenances. Identified valve actuation as root cause and received recommendation for organizational award.}
                \resumeItem{Detected water main breaks, manually isolated valves, and supervised crew during open excavation and main replacement. Liaised with city stakeholders and regional office to address service interruption.}
                % \resumeItem{Assessed residential and commercial water meter on scheduled and emergency basis. Troubleshooted meter reading signals, repaired wiring and replaced appurtenances.}
                % \resumeItem{Devised and executed a unidirectional water main flushing plan. Coordinated with operations team to isolate water main section in order for contractors to launch and retrieve swabs. Tested for water bacteriological and disinfectant levels to ensure safe drinking water.}
            \resumeItemListEnd

        % POSITION 3
        \resumeSubheading
        {Project Coordinator}{Mississauga, ON}
            % COMPANY 3
            {Certified Building Systems}{07/2016 - 05-2018}
            \resumeItemListStart
                \resumeItem{Managed project portfolio and coordinated resources for existing high-rise HVAC retrofits and successfully delivered projects individually valued at up to \$750,000. Steered end-to-end project progress from purchasing, installation, commissioning and hand-off.}
                \resumeItem{Accomplished complex and time-sensitive crane lift operations for heating and cooling plants. Negotiated on-site pivots to lift sequencing in order to adapt to staging issues, delivery delays and inclement weather. Delegated project team and communicated with property management while minimizing impact on residents and surrounding stakeholders.}
                % \resumeItem{Researched viable alternatives for equipment purchasing based on client tender requirements and engineer recommendations to provide competitively priced bids. Verified project progress through regular site inspections and reconcile deficiencies with in-house technicians and contractors.}
            \resumeItemListEnd

        % % % POSITION 4
        % \resumeSubheading
        % {Project Associate}{Toronto, ON}
        %     % COMPANY 4
        %     {WSP (formerly Halsall and Associates)}{07/2016 - 05-2018}
        %     \resumeItemListStart
        %         \resumeItem{Performed commercial ASHRAE Level 2 energy audit by reviewing utility data, system schematics, and building automation system (BAS) trends to yield annual savings of \$270,000 and 3,200 MWh.}
        %         \resumeItem{Conducted water audit for Class A office building by analyzing
        %         billing/sub-metering data and consulted stakeholders. Recommended
        %         water conservation plan for energy and monetary savings.}
        %         \resumeItem{Researched green infrastructure initiatives and outlined multi-tier strategies for commercial clients to achieve LEED framework sustainability targets. Tracked energy, water, waste, transportation, indoor air quality, environment and occupant metrics.}
        %     \resumeItemListEnd
            
    \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  PROJECTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Personal Projects} 
    \resumeSubHeadingListStart

        % Position 1
        \resumeSubheading
        {gattaGo -\href{https://github.com/kimcangho/gattaGo-client}{\raisebox{-0.2\height}\ \faGithub\ \underline{CODE}}}{}
            {TypeScript, React, TailwindCSS, Node.js, Express.js, Prisma, MySQL}{05/2023 - 09/2023}
            \resumeItemListStart
                \resumeItem{Dragonboat racing team builder with dashboard display, athlete management, lineup assignment, and race plan crafting features with custom REST API. Integrated third-party chart, drag-and-drop and mapping libraries.}
            \resumeItemListEnd

            
        % Project 2
        \resumeSubheading
        {Squiggled -\href{https://github.com/kimcangho/squiggled-client}{\raisebox{-0.2\height}\ 
        \faGithub\ \underline{CODE}} -\href{https://squiggled.netlify.app/}{\raisebox{-0.2\height}\ \faGlobe\ \underline{SITE}}
        }{}
            {JavaScript, React, SASS, Node.js, Express.js, Socket.io}{12/2022 - 01-2023}
            \resumeItemListStart
                \resumeItem{Peer-to-peer whiteboarding web application allowing users to capture, annotate, send and download screenshots from their device camera. Integrated native camera API for image capture with WebSocket server for user interactions.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%  Education  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
  \resumeSubHeadingListStart
  
    % MAIN INFORMATION
    \resumeSubheading
    {University of Waterloo}{Waterloo, ON}
    {Honours Bachelors of Applied Science in Mechanical Engineering}{09/2010 - 04/2015}

    %  % MAIN INFORMATION
    % \resumeSubheading
    % {Fleming College}{Lindsay, ON}
    % {Graduate Certificate - Advanced Water Systems Operations and Management}{09/2018 - 08/2019}

     % MAIN INFORMATION
    \resumeSubheading
    {BrainStation}{Toronto, ON}
    {Diploma - Web Development}{09/2022 - 12/2022}
  \resumeSubHeadingListEnd

  \end{document}
